Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-16 doc/main_jfm.tex
token
finished section 3.3

\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{commath}
\usepackage{todonotes}

@@

% Bryan's Marcros
\renewcommand{\aa}{\mathbf{a}}
\newcommand{\bd}{\partial}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\eeta}{\boldsymbol{\eta}}
\newcommand{\FF}{\mathbf{F}}
\newcommand{\GG}{\mathbf{G}}
\newcommand{\JJ}{\mathbf{J}}
\newcommand{\nnu}{\boldsymbol{\nu}}
\newcommand{\ssigma}{\boldsymbol{\sigma}}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\RR}{\mathbf{R}}
\renewcommand{\SS}{\mathbf{S}}
\newcommand{\xx}{\mathbf{x}}
\newcommand{\XX}{\mathbf{X}}
\newcommand{\uu}{\mathbf{u}}
\renewcommand{\vv}{\mathbf{v}}
\newcommand{\yy}{\mathbf{y}}
\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}

@@

\section{Governing  Equations\label{sec:governing_eqs}}
\subsection{\label{mobility}Mobility Problem}
We consider a suspension of $N_b$ particles suspended in a
two-dimensional unbounded domain. The boundary of each particle is
denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup \Gamma_2 \cup
\cdots \cup \Gamma_{N_b}$. Assuming the flow is Stokesian, the governing
equations are
\begin{alignat}{3}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $\mu$ is viscosity, $p$ is the pressure,
and $\uu_\infty$ is the background flow. Since each particle $\Gamma_i$
with center $\aa_i$ is a rigid body, its velocity satisfies 
\begin{align}
  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$. Therefore, the no-slip boundary condition on each particle is
\begin{align}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
    \xx \in \Gamma_i.
\end{align}
To determine the translational and angular velocities of each particle,
we assume some imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are intertialess, force balance
gives 
\begin{alignat}{2}
  \label{eqn:force}
  \FF_i &+ \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eqn:torque}
  T_i &+ \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu_i) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor). The
process of finding the translational and angular velocities given a
force and torque is referred to as the mobility problem.

\subsection{Imposed Forces}
The imposed forces and torques contain two parts. The first part comes
from the hydrophobic attraction potential (HAP). This potential was
introduced in~\cite{Fu20} and models hydrophobic attraction by solving
the screened Laplace equation boundary value problem
\begin{alignat}{2}
  \label{SL}
-\rho^2 \Delta u + u &=0,            && \xx \in \Omega,\\
\label{SLbc}
u(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i, \\
\label{SLff}
u &\to 0,                          &&|\xx| \to \infty,
\end{alignat}
where $f_i$ is a material label with $f_i = 0$ ($1$) representing
hydrophilic (hydrophobic) portions of the surface, and $\rho$ is the
decay length of attraction. The forces and torques for this attraction
are 
\begin{align}
  \label{eqn:hydrophobicAttraction}
  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu_i \, \dif s, 
    \quad 
  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu_i) \dif s,
\end{align}
where
\begin{align}
  \label{eq:stress}
\mathbf{T}
= \gamma\rho^{-1}u^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
  u|^2 \mathbf{I} - \nabla u  \nabla u^T\right)
\end{align}
is the hydrophobic stress tensor. The parameter $\gamma$ is interfacial
tension. The forces $\FF_i^{\text{hydro}}$ and torques
$T_i^{\text{hydro}}$ are responsible for forming particle aggregates
that partially sequester the hydrophobic portions of the particle
surface.

@@

\subsection{HAP Boundary Integral Equation}
Similar to our previous work~\cite{Fu20}, we represent the HAP as a
double-layer potential
\begin{align}
  \label{eqn:HAP_DLP}
  u(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \Omega,
\end{align}
where $K_0$ is the zeroth-order modified Bessel function of the first
kind. By requiring that the density function $\sigma$ satisfies the
second-kind integral equation
\begin{align}
  f(\xx) = \frac{1}{2}\sigma(\xx) + 
    \frac{1}{2\pi}\int_{\bd\Omega} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \bd\Omega,
\end{align}
the HAP double-layer potential~\eqref{eqn:HAP_DLP} satisfies the
screened Laplace equation~\eqref{SL}--\eqref{SLff}. To calculate the
hydrophobic force and torque, the gradient of the double-layer
potential~\eqref{eqn:HAP_DLP} must be computed on the boundary of each
particle. In Section~\ref{subsec:calculating_force}, we show that the force and
torque calculations can be expressed in terms of integral that are
non-singular.

\subsection{Mobility Problem Boundary Integral Equation}
Following previous work of~\cite{Lukas19}, we represent the velocity as
the sum of a double-layer potential and the $N_b$ Stokeslets and Rotlets
\begin{align}
  \label{eqn:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
\end{align}
The double-layer potential is
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nnu}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
    \eeta(\yy) \, \dif s_\yy,
\end{align}
where $\rr = \xx - \yy$ and $\rho = |\rr|$. The Stokeslet and Rotlet
centered at $\aa_i$ are
\begin{align}
  \SS(\xx,\aa_i)\FF_i &= \frac{1}{4\pi} \left(-\log(\rho) + 
    \frac{\rr \otimes \rr}{\rho^2} \FF_i \right), \\
  \RR(\xx,\aa_i)T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{\rho^2} T_i,
\end{align}
where $\rr = \xx - \aa_i$ and $\rho = |\rr|$. The Stokeslet is
torque-free and has force $\FF_i$ while the Rotlet force-free and has
torque $T_i$. Therefore, the velocity~\eqref{eqn:velocity} satisfies the
total force~\eqref{eqn:force} and torque~\eqref{eqn:torque} conditions
if the double-layer potential $\DD[\eeta]$ is force- and torque-free.
Matching the limit of~\eqref{eqn:velocity} with the rigid body motion,
and imposing that $\DD[\eeta]$ is force- and torque-free, the density
function $\eeta$, translational velocity $\vv_i$, and angular velocity
$\omega_i$ satisfy
\begin{alignat}{3}
  \nonumber
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
  \label{eqn:SKIE}
    + \sum_{j=1}^{N_b} &
    \left(\SS(\xx,\aa_j) \FF_j + \RR(\xx,\aa_j) T_j\right),
    \quad &&\xx \in \bd \Gamma_i,\: i=1,\ldots,N_b, \\
  \label{eqn:mobility1}
  \int_{\bd\Gamma_i} \eeta \cdot \nnu_i \, \dif s &= {\bf 0}, 
  &&i = 1,\ldots,N_b, \\
  \label{eqn:mobility2}
  \int_{\bd\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu \, \dif s &= 0,
  &&i = 1,\ldots,N_b.
\end{alignat}

@@

\subsection{Calculating the Hydrophobic Force}
\label{subsec:calculating_force}
The stress \eqref{eq:stress} contains
contains the gradient of the double-layer potential \eqref{eqn:HAP_DLP},
making it difficult to evaluate
the forces and torques \eqref{eqn:hydrophobicAttraction}.
The identities \eqref{eq:recipforcetorque}
make it possible to evaluate the forces and torques
without specialized quadrature methods.

Consider the particle
$\Gamma_i$ indexed by $i$
and decompose $u$ as follows: 
\begin{equation}
u = u_i + v_i
\end{equation}
where  
\begin{equation}
    u_i(\xx) = \frac{1}{2\pi} \int_{\Gamma_i} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \Omega.
\end{equation}
That is, $u_i$ is the double-layer potential for the restriction of $\sigma$ to $\Gamma_i$.  Let $\FF_i$ and $T_i$ be as in \eqref{eqn:hydrophobicAttraction}. We prove that 
\begin{equation}
\label{eq:recipforcetorque}
\FF_i= \int_{\Gamma_i} \JJ_i \,\dif s,\quad
T_i= \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot \JJ_i  \,\dif s
\end{equation}
where
 \begin{equation}
\label{eq:jumpstress1}
\JJ_{i} = 2\gamma\left[\rho^{-1} u v_i \nnu 
+ \rho \nabla u \cdot \tau (\nabla v_i \cdot \tau \nnu -  \nabla
   v_i \cdot \nnu \tau)\right].
\end{equation}
Here $\nnu$ is the unit normal and $\tau$ is a unit tangent vector.
Observe that  $u$ and $\nabla u \cdot \tau$ come from the boundary data $f_i$ \eqref{SLbc} and are smooth. The functions $v_i$ and $\nabla v_i$
come from double-layer integrals that are smooth on $\Gamma_i$.

To prove \eqref{eq:recipforcetorque},
let \begin{align*}
  {\bf T}
  &=
  \sigma[u_i,u_i]
  +(\sigma[u_i,v_i]
  +\sigma[v_i,u_i])
  +\sigma[v_i,v_i] \\
  &= {\bf T}_1 + {\bf T}_2 + {\bf T}_3
\end{align*}
where we have introduced the notation
\[
\sigma[u,v]
= \rho^{-1} uv {\bf I} + \rho \nabla u \cdot \nabla v {\bf I} - 2 \rho \nabla u \nabla v^T.
\]
Using the fact that $u$, $u_i$, and $v_i$ solve the equation
$-\rho^2 \Delta u + u = 0$, and that ${\bf T}$ is symmetric,
it is straightforward to show that 
  \begin{equation}
    \label{eq:decompdivfree}
    \nabla \cdot {\bf T}_j = 0, \quad
    \nabla \cdot (\xx \times {\bf T}_j) = 0,\quad j = 1, 2, 3.
  \end{equation}

\begin{lemma}
  \label{eq:stress_div_lemma}
  \begin{equation}
    \label{eq:decompdivfree}
    \nabla \cdot {\bf T}_j = 0, \quad
    \nabla \cdot (\xx \times {\bf T}_j) = 0,\quad j = 1, 2, 3.
  \end{equation}
\end{lemma}
\begin{proof}
  The function $u$ solves $-\rho^2 \Delta u + u = 0$. Using the summation convention, 
  \begin{align*}
    (\nabla \cdot {\bf T})_j &=
    \nabla_k   T_{jk} \\
    &= \rho^{-1} 2u \nabla_j u + \rho(2\nabla_{kl}^2 u \nabla_l u  - 2 \nabla_{kj}^2 u \nabla_k u
    - 2 \nabla_j u \nabla_{kk}^2 u )\\
    &=2\rho^{-1}(-\rho^2 \Delta u + u)\nabla_k u = 0.
  \end{align*}
Moreover, 
  \begin{align*}
    (\nabla \cdot (\xx \times {\bf T} ))_j
    &= \nabla_k (\epsilon_{jml}x_m T_{lk})\\
    &= \varepsilon_{jml} T_{lm} + \varepsilon_{jml}x_m \nabla_k T_{lk}\\
    &= (\boldsymbol{\varepsilon}:{\bf T} + {\bf x} \times \nabla \cdot {\bf T})_j.
  \end{align*}
  where $\varepsilon_{jml}$ is the alternating tensor. 
  Since ${\bf T}$ is symmetric $\boldsymbol{\varepsilon}:{\bf T} = {\bf 0}$, and we get
  $\nabla \cdot (x \times {\bf T}) = 0$ as well.

  The functions $u_p$ and $v_p$ also solve the equation $-\rho^2 \Delta u + u = 0$.  Thus
  \eqref{eq:decompdivfree} holds for $j = 1, 3$. Finally,
  \eqref{eq:decompdivfree} holds for $j = 2$ because
  ${\bf T}_2 = {\bf T} - {\bf T}_1 - {\bf T}_3$.
\end{proof}

Using Lemma \ref{eq:stress_div_lemma}, we will establish that
\begin{equation}
  \label{eq:prejump}
  F_p + i G_p = \gamma \int_{\Sigma_p}  ({\bf U}_2\nnu)^+ - ({\bf
  U}_2\nnu)^-\,\dif S
\end{equation}
where ${\bf U}_j = ({\bf I} + i {\bf X}){\bf T}_j$ for $j = 1, 2, 3.$
The stress ${\bf U}_2$ has a jump discontinuity at $\Sigma_p.$
The plus and minus superscripts denote
the limit taken along points in $U_p^c$ and along points in $U_p$
respectively.
${\bf U}_1$ and ${\bf U}_3$ are real-analytic in a neighborhood of $\overline{U_p}$
and have no jump-discontinuity at $\Sigma_p$.
To derive \eqref{eq:prejump}, we expand
\begin{align*}
  F_p + i G_p
  &= \gamma \int_{\Sigma_p} {\bf T} \nnu + ix \times {\bf T} \nnu \,\dif S \\
  &= \gamma \int_{\Sigma_p}  {\bf U}_1\nnu  + ({\bf U}_2\nnu)^+ + {\bf
  U}_3\nnu\,\dif S
\end{align*}
The function $u_p$ is real-analytic and
$\nabla \cdot {\bf U}_1 = 0$ throughout $\mathbb{R}^n \setminus U_p$.
By the divergence theorem, we get
\begin{equation*}
  \int_{\Sigma_p}  {\bf U}_1 \nnu\,\dif S
  = \int_{\mathbb{R}^n \setminus U_p} \nabla \cdot {\bf U}_1 \,dx = 0.
\end{equation*}
Next, $v_p$ is real-analytic and
$\nabla \cdot {\bf U}_3 = 0$ in $U_p$. Therefore
\begin{equation*}
  \int_{\Sigma_p}  {\bf U}_3 \nnu\,\dif S
  = -\int_{U_p} \nabla \cdot {\bf U}_3 \,dx = 0.
\end{equation*}
Finally, $\nabla \cdot {\bf U}_2= 0$ in $U_p$. This gives
\[
0 = -\int_{U_p} \nabla \cdot {\bf U}_2 \,dx = \int_{\Sigma_p}  ({\bf
U}_2 \nnu)^-\,\dif S.
\]
Combining the last four equations give \eqref{eq:prejump}.

>>>>

\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{commath}
\usepackage{todonotes}
%

@@

% Bryan's Marcros
\renewcommand{\aa}{\mathbf{a}}
\newcommand{\bd}{\partial}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\eeta}{\boldsymbol{\eta}}
\newcommand{\FF}{\mathbf{F}}
\newcommand{\GG}{\mathbf{G}}
\newcommand{\JJ}{\mathbf{J}}
\newcommand{\nnu}{\boldsymbol{\nu}}
\newcommand{\ttau}{\boldsymbol{\tau}}
\newcommand{\ssigma}{\boldsymbol{\sigma}}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\RR}{\mathbf{R}}
\renewcommand{\SS}{\mathbf{S}}
\newcommand{\xx}{\mathbf{x}}
\newcommand{\XX}{\mathbf{X}}
\newcommand{\uu}{\mathbf{u}}
\renewcommand{\vv}{\mathbf{v}}
\newcommand{\yy}{\mathbf{y}}
\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}

@@

\section{Governing  Equations\label{sec:governing_eqs}}
\subsection{\label{mobility}Mobility Problem}
We consider an $N_b$-many body collection of particles suspended in a
two-dimensional unbounded domain $\Omega$. The boundary of each particle is
denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup \Gamma_2 \cup
\cdots \cup \Gamma_{N_b}$ and $\nnu_i$ is the particle outward normal. 
Assuming the flow is Stokesian, the governing
equations are
\begin{alignat}{3}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $\mu$ is viscosity, $p$ is the pressure,
and $\uu_\infty$ is the background flow. Since each particle $\Gamma_i$
with center $\aa_i$ is a rigid body, its velocity satisfies 
\begin{align}
  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$. Therefore, the no-slip boundary condition on each particle is
\begin{align}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
    \xx \in \Gamma_i.
\end{align}
To determine the translational and angular velocities of each particle,
we assume some imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are intertialess, force balance
gives 
\begin{alignat}{2}
  \label{eqn:force}
  \FF_i &+ \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eqn:torque}
  T_i &+ \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu_i) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor).
The process of finding the translational and angular velocities given a
force and torque is referred to as the mobility problem.

\subsection{Imposed Forces}
The imposed forces and torques contain two parts. The first part comes
from the hydrophobic attraction potential (HAP). This potential was
introduced in~\cite{Fu20} and models hydrophobic attraction by solving
the screened Laplace equation boundary value problem
\begin{alignat}{2}
  \label{SL}
-\rho^2 \Delta u + u &=0,            && \xx \in \Omega,\\
\label{SLbc}
u(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i, \\
\label{SLff}
u &\to 0,                          &&|\xx| \to \infty,
\end{alignat}
where $f_i$ is a material label with $f_i = 0$, respectively $1$, representing
hydrophilic, respectively hydrophobic, portions of the surface, and $\rho$ is the
decay length of attraction. The forces and torques for this attraction
are 
\begin{align}
  \label{eqn:hydrophobicAttraction}
  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu_i \, \dif s, 
    \quad 
  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu_i) \dif s,
\end{align}
where
\begin{align}
  \label{eq:stress}
\mathbf{T}
= \gamma\rho^{-1}u^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
  u|^2 \mathbf{I} - \nabla u  \nabla u^T\right)
\end{align}
is the hydrophobic stress tensor. The parameter $\gamma$ is interfacial
tension. The forces $\FF_i^{\text{hydro}}$ and torques
$T_i^{\text{hydro}}$ are responsible for forming particle aggregates
that partially sequester the hydrophobic portions of the particle
surface.

@@

\subsection{HAP Boundary Integral Equation}
Similar to our previous work~\cite{Fu20}, we represent the HAP as a
double-layer potential
\begin{align}
  \label{eqn:HAP_DLP}
  u(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \Omega,
\end{align}
where $K_0$ is the zeroth-order modified Bessel function of the first
kind. By requiring that the density function $\sigma$ satisfies the
second-kind integral equation
\begin{equation}
\label{eq:SKIE}
  f(\xx) = \frac{1}{2}\sigma(\xx) + 
    \frac{1}{2\pi}\int_{\bd\Omega} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \bd\Omega,
\end{equation}
the HAP double-layer potential~\eqref{eqn:HAP_DLP} satisfies the
screened Laplace equation~\eqref{SL}--\eqref{SLff}. To calculate the
hydrophobic force and torque, the gradient of the double-layer
potential~\eqref{eqn:HAP_DLP} must be computed on the boundary of each
particle. In Section~\ref{subsec:calculating_force}, we show that the force and
torque calculations can be expressed in terms of integral that are
non-singular.

\subsection{Mobility Problem Boundary Integral Equation}
Following previous work of~\cite{Lukas19}, we represent the velocity as
the sum of a double-layer potential and the $N_b$ Stokeslets and Rotlets
\begin{align}
  \label{eqn:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
\end{align}
The double-layer potential is
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nnu}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
    \eeta(\yy) \, \dif s_\yy,
\end{align}
where $\rr = \xx - \yy$ and $\rho = |\rr|$. The Stokeslet and Rotlet
centered at $\aa_i$ are
\begin{align}
  \SS(\xx,\aa_i)\FF_i &= \frac{1}{4\pi} \left(-\log(\rho) + 
    \frac{\rr \otimes \rr}{\rho^2} \FF_i \right), \\
  \RR(\xx,\aa_i)T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{\rho^2} T_i,
\end{align}
where $\rr = \xx - \aa_i$ and $\rho = |\rr|$. The Stokeslet is
torque-free and has force $\FF_i$ while the Rotlet force-free and has
torque $T_i$. Therefore, the velocity~\eqref{eqn:velocity} satisfies the
total force~\eqref{eqn:force} and torque~\eqref{eqn:torque} conditions
if the double-layer potential $\DD[\eeta]$ is force- and torque-free.
Matching the limit of~\eqref{eqn:velocity} with the rigid body motion,
and imposing that $\DD[\eeta]$ is force- and torque-free, the density
function $\eeta$, translational velocity $\vv_i$, and angular velocity
$\omega_i$ satisfy
\begin{alignat}{3}
  \nonumber
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
  \label{eqn:SKIE}
    + \sum_{j=1}^{N_b} &
    \left(\SS(\xx,\aa_j) \FF_j + \RR(\xx,\aa_j) T_j\right),
    \quad &&\xx \in \bd \Gamma_i,\: i=1,\ldots,N_b, \\
  \label{eqn:mobility1}
  \int_{\bd\Gamma_i} \eeta \cdot \nnu_i \, \dif s &= {\bf 0}, 
  &&i = 1,\ldots,N_b, \\
  \label{eqn:mobility2}
  \int_{\bd\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu_i \, \dif s &= 0,
  &&i = 1,\ldots,N_b.
\end{alignat}

@@

\subsection{Calculating the Hydrophobic Force}
\label{subsec:calculating_force}
Once \eqref{eq:SKIE} has been solved and $\sigma$ determined,
we can evaluate the integrals  \eqref{eqn:hydrophobicAttraction}. 
These integrals involve the stress \eqref{eq:stress} which contains
a singular integral for the gradient of the double-layer potential.   
To avoid singular integrals, we use the alternative forms
\begin{equation}
\label{eq:recipforcetorque}
\FF_i^{\text{hydro}} = \int_{\Gamma_i} \JJ_i \,\dif s,\quad
T_i^{\text{hydro}}    = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot \JJ_i  \,\dif s
\end{equation}
where
 \begin{equation}
\label{eq:jumpstress1}
\JJ_{i} =2\gamma\rho^{-1} \sigma v_i \nnu + 2\gamma\rho \frac{d\sigma }{ds}\frac{dv_i }{ds} \nnu
    - 2\gamma\rho \ \frac{d\sigma }{ds} \frac{dv_i }{d\nu} \ttau.
\end{equation}
Here, $\ttau$ and $\frac{d}{ds}$ are the unit tangent  and arc length  derivative for $\Gamma_i$, respectively, 
and
\begin{equation}
\label{eq:uidef}
    v_i(\xx) = u(\xx) - \frac{1}{2\pi} \int_{\Gamma_i} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \Omega.
\end{equation}
The advantage in using \eqref{eq:jumpstress1} over \eqref{eq:stress} 
is that components $\sigma$, $v_i$, $\frac{d\sigma}{ds}$, and  $\frac{dv_i}{ds}$ are all smooth.

To prove \eqref{eq:recipforcetorque},
let \begin{align*}
  {\bf T}
  &=
    \mathbf{S}(u_i,u_i)
  +(\mathbf{S}(u_i,v_i)
  +\mathbf{S}(v_i,u_i))
  +\mathbf{S}(v_i,v_i) \\
  &= {\bf T}_1 + {\bf T}_2 + {\bf T}_3
\end{align*}
where we introduce the bilinear form
\begin{equation}
\label{eq:Tsplit}
\mathbf{S}(u,v)
=  \gamma\rho^{-1} uv {\bf I} + \gamma\rho \nabla u \cdot \nabla v {\bf I} - 2 \gamma \rho \nabla u \nabla v^T .
\end{equation}
Using the fact that $u$,  $u_i$, and $v_i$ solve the equation $-\rho^2 \Delta u + u = 0$,
and that $\mathbf{T}$, $\mathbf{T}_j$, $j = 1, 2, 3$ are symmetric, it is straightforward to verify that 
  \begin{equation}
    \label{eq:decompdivfree}
    \nabla \cdot {\bf T}_j = 0, \quad
    \nabla \cdot ((\xx-\aa_i)^{\perp} \cdot {\bf T}_j) = 0, \quad j = 1, 2, 3.
  \end{equation}

%\begin{lemma}
%  \label{eq:stress_div_lemma}
%  \begin{equation}
%    \label{eq:decompdivfree}
%    \nabla \cdot {\bf T}_j = 0, \quad
%    \nabla \cdot (\xx^{\perp} \cdot {\bf T}_j) = 0
%  \end{equation}
% for  $ j = 1, 2, 3$.
%\end{lemma}
%\begin{proof}
%  Let $\mathbf{T}$ be as in \eqref{eq:stress}.  
%  It is straightforward to show that  
%%  \begin{align*}
% %   (\nabla \cdot {\bf T})_j &=
% %   \nabla_k   T_{jk}  = 0\\
% %   &= \rho^{-1} 2u \nabla_j u + \rho(2\nabla_{kl}^2 u \nabla_l u  - 2 \nabla_{kj}^2 u \nabla_k u
% %  - 2 \nabla_j u \nabla_{kk}^2 u )\\
% %   &=2\rho^{-1}(-\rho^2 \Delta u + u)\nabla_j u = 0,
% % \end{align*}
% \begin{equation*}
%\nabla \cdot {\bf T} = 2\rho^{-1}(-\rho^2 \Delta u + u)\nabla u = 0
% \end{equation*}
% since $u$ solves $-\rho^2 \Delta u + u = 0$.
% Moreover,
%  \begin{align*}
%    \nabla \cdot (\xx^{\perp} \cdot {\bf T} )
%%    &= \nabla_k (\epsilon_{jml}x_m T_{lk})\\
%%    &= \varepsilon_{jml} T_{lm} + \varepsilon_{jml}x_m \nabla_k T_{lk}\\
%%   &= (\boldsymbol{\varepsilon}:{\bf T} + {\bf x}^{\perp} \cdot \nabla \cdot {\bf T})_j.
%=  \mathbf{S}:\mathbf{T} + \mathbf{S}\xx \cdot (\nabla \cdot \mathbf{T}) = 0,
%  \end{align*}
%  since ${\bf T}$ is symmetric, where $\mathbf{S}\xx = \xx^{\perp}$.
%  
%  The functions $u_i$ and $v_i$ also solve the equation $-\rho^2 \Delta u + u = 0$.  Repeating the above argument 
%  for ${\bf T}_1 = \sigma[u_i,u_i]$ and ${\bf T}_3 = \sigma[v_i,v_i]$ gives that 
%  \eqref{eq:decompdivfree} holds for the cases $j = 1$ and $j = 3$. Finally,
%  \eqref{eq:decompdivfree} holds for the case $j = 2$ because
%  ${\bf T}_2 = {\bf T} - {\bf T}_1 - {\bf T}_3$.
%\end{proof}

Let $U_i$ be the interior of the particle indexed by $i$. 
For $\xx_0 \in \Gamma_i$ and an arbitrary function $g(\xx)$, the notation
\begin{equation}
\lim_{\xx \to \xx_0^+}g(\xx),\quad 
\lim_{\xx \to \xx_0^-}g(\xx), \quad
[g](\xx_0) = \lim_{\xx \to \xx_0^+}g(\xx)  - \lim_{\xx \to \xx_0^-}g(\xx)
\end{equation}
denotes the limit taken from points in $U_i^c$,  the limit taken from points in $U_i$, and the jump, respectively.  
\begin{lemma}
\begin{equation}
  \label{eq:prejump}
\FF_i = \int_{\Gamma_i} [{\bf T}_2  \nu_i]  \, \dif s,\quad
T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot [{\bf T}_2 \nu_i] \, \dif s.
\end{equation}
\end{lemma}
\begin{proof}
To derive \eqref{eq:prejump}, we expand
\begin{equation*}
  \FF_i 
  = \int_{\Gamma_i}  {\bf T}_1\nnu  + {\bf T}_2\nnu + {\bf   T}_3\nnu\,\dif s.
\end{equation*}
By \eqref{eq:uidef} and \eqref{eq:decompdivfree}, we have $u_i$ smooth and  
$\nabla \cdot {\bf T}_1 = \mathbf{0}$ in $\mathbb{R}^n \setminus U_i$.
Similarly, $v_i = u - u_i$ is smooth and
$\nabla \cdot {\bf T}_3 = \mathbf{0}$ in $U_i$. 
By the divergence theorem,  
\begin{equation*}
  \int_{\Gamma_i}  {\bf T}_1\nnu \,\dif s
  = -\int_{\mathbb{R}^n \setminus U_i} \nabla \cdot {\bf T}_1 \,dx = \mathbf{0},\quad
    \int_{\Gamma_p}  {\bf T}_3 \nnu\,\dif s
  = \int_{U_p} \nabla \cdot {\bf T}_3 \,dx = \mathbf{0}.
\end{equation*}
Finally, $\nabla \cdot {\bf T}_2= 0$ in $U_i$. This gives
\[
\mathbf{0} = \int_{U_i} \nabla \cdot {\bf T}_2 \,dx = -\int_{\Gamma_i}  ({\bf T}_2 \nnu)^-\,\dif s,
\]
where the superscript denotes the limit taken from in $U_i$.  
Combining the previous four equations gives the first equation in \eqref{eq:prejump}.
The argument for the second equation in \eqref{eq:prejump} is identical. 
\end{proof}
